\documentclass[runningheads]{llncs}


\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\urlstyle{same}
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{listings}
\lstdefinestyle{Bash}
{language=bash,
keywordstyle=\color{blue},
basicstyle=\ttfamily,
morekeywords={setX},
alsoletter={:~$}
morekeywords=[2]{setX:},
keywordstyle=[2]{\color{red}},
literate={\$}{{\textcolor{red}{\$}}}1 
         {!}{{\textcolor{red}{!}}}1
         {~}{{\textcolor{red}{\textasciitilde}}}1,
}

\usepackage{amsmath}
\usepackage{cleveref}       % smart cross-referencing, load after amsmath

% This LaTeX Document is intended to be used on Overleaf 

\usemintedstyle{vs}
\usepackage[dvipsnames]{xcolor}
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:

\begin{document}



\title{Procedural approaches towards Maximal Extracted Value}
%
\author{Alexander Sandy Bradley\inst{1,2} \and
	Sam Bacha\inst{1,2} \and
	et al\inst{1}}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Manifold Finance, Inc\and CommodityStream, Ltd.\\
	\email{\{sandy,sam\}@manifoldfinance.com}\\
	\email{janitor@manifoldfinance.com}}

\maketitle
\begin{abstract}

mev succ.\footnote{Bacha, Sam "MEV is essentially looking for the reachable state where their balance is maximized. Given any arbitrary re-ordering, insertion or censorship of pending or existing transactions, this can suck, suck real hard."}
sandwhich sucks.
protecc usr. 
use openmev. \cite{openmev}.

\keywords{MEV, \and Miner Extractable Value \and trade optimization, \and EVM \and uniswap \and sushiswap \and ethereum \and formal verification}
\end{abstract}


\section{Overview}
	\textbf{MEV is sucks. }\newline
 MEV or Maximal Extractable Value is the value of the ability to order transactions within a block or blocks\footnote{Tom Schmidt, Dragonfly Capital}
	\newline
\section{Motivation}
\text{see} \textbf{\emph{Abstract}}. 

\subsubsection{The MEV Killchain} 
An actor who can influence the order in which transactions are included in a block can affect the economic outcome of trades. The audit team is aware of two strategies for profitably exploiting this fact. Such strategies can be used not only by miners but also by any party who is able to observe unconfirmed transactions and submit their own transactions with carefully chosen gas prices. The router includes some features that provide some degree of protection against the first strategy, but no such mitigation's exist for the second.

\subsection{Transaction time-dependence}
Transaction reordering and front-running attacks can arguably be viewed as a broader structural problem inherent to many trading venues both with on-chain clearing and settlement and in legacy capital markets. 
\footnote{Such strategies have been widespread in Ethereum for many years, and the rents accruing to miners from the transaction reordering privilege (miner extractable value) can even pose a threat to the security of the blockchain consensus layer.}

By following the flow of balances, we observe that the aggregate economic effect of the sandwiching was equivalent to a trade between the front-runner and the trader (with the pool ending up back where they started, having only collected fees from the 3 transactions), however the front-runner was able to effectively choose the price at which the trade happens by choosing the size of their first trade, and so is able to set the price arbitrarily in their own favor. 
\newline

To see that this can still be profitable in the presence of LP fees, it suffices to observe that while LP fees paid by the front-runner are proportional to the size of the sandwich trade, the price impact of the sandwich trade on the Pair's price is quadratic in the size of the sandwich trade, meaning that the sandwich can be made profitable with a sufficiently large manipulating trade, and the trader's loss is only limited by the value of their trade.

\subsection{Just in Time Liquidity Attacks}
In this second variant, the attacker watches for large trades, and sandwiches the target trade with calls to mint and burn with a very large position relative to the initial size of the pool. The attacker is therefore able to extract a sizeable proportion of the LP fees for that trade without exposing themselves to the price risk inherent to providing liquidity on Uniswap.

\subsection{Known Vectors of Attack}
Neither the core nor the periphery contracts contain guards against this attack, and the audit team is not aware of any straightforward solution. A minimum lock lock time for liquidity providers, imposed in the core, could potentially help to reduce the profits siphon-able with this attack.\footnote{See https://etherscan.io/token/0x05934eba98486693aaec2d00b0e9ce918e37dc3f#tokenTrade}
\newpage 
\subsection{Current Mitigations}
The methods exposed on the user-facing UniswapV2Router02 contract contain arguments that allow callers to impose off-chain slippage limits on their orders (AmountOutMin, AmountOutMax), and when set appropriately these parameters can limit the losses to trader front-running. Note however that it might not be possible to eliminate front-running entirely with this technique, since setting the slippage limit too tightly to the market could result in a poor success rate, with the market moving against the trader.\footnote{Deadline, or the expiry of the trade, can also be used to mitigate the risk of front-running.}

\subsection{Targeted Attacks}
It has been observed and reported non-economic manipulations of UniswapV2 and SushiswapV01 markets to derive a competitive advantage against other tokens / assets trading. Care has been taken to make the implementation not use or be ab usable by such tokens. A notable example is the effect of rebasing tokens on volume measures. A protocol called DELTAV1\cite{Bacha 2022} was banned from UniswapV2's frontend interface for 'manipulating' their frontend. Afterwards Uniswap took the unilateral action to ban any rebase token from showing on volume measures on their analytics or frontend.

\subsection{Desirable Security properties}
In following the standards set forth by the UniswapV02 and SushiswapV01 router contracts, the SushiswapV02 router contracts are intended to be safe to use with:

\begin{itemize}
  \item Potentially reentrant tokens
  \item Tokens that do not return from transfer
  \item Pathological Tokens The SushiswapV02 router contracts are not intended to be used tokens that exhibit the following behavior
  \item Tokens that exhibit a discretizing inflation curve
  \item Tokens that exhibit an 'unowned' supply
  \item Tokens that implement user defined types for standard mathematical operations
  \item Numerical error analysis The engineering team would like to request a review of the numerical error incurred during contract execution, with a focus on the desirable invariant proposed by both the development team and auditors. \footnote{Examples include any significant rounding error, if any, in a swap, favors the pool. etc.}
\end{itemize}

\newpage
\section{Requirements}

\subsection{Design and Implementation }
\paragrah{The Original design for the router was to use flashloans only to arbitrage then immediately distribute profits to hard coded addresses. Apart from the issue of hard coded addresses, this setup was inefficient because of small amounts frequently being split and transferring to multiple addresses being expensive. This opened the possibility of leaving profits to accumulate on the router. Furthermore it provides a way to arbitrage without a flashloan, saving gas and the loan fee (i.e. more profit, less gas). Additionally, the harvesting profits means ownership control of the router. A more robust 2 step process was chosen to control and transfer router ownership and harvest control. Ideal setup would be multisig consensus ownership.}\footnote{Ownership control of the router is not an issue, as a new router can be used or fallback to the legacy router contract.}

\subsection{Optimal Routing}
Optimal routing problem. We wish to find a set of valid trades that maximizes the trader's utility.\cite{Angiers 2021, Optimal Routing for Constant Function Market Makers}

\subsection{Conformant Algorithms}

Conformant Algorithms
Our requirements are phrased in the imperative, as such, part of algorithms (such as "strip any leading space characters" or "return false and abort these steps") are to be interpreted with the meaning of the RFC/EIP defined key words ("must", "should", "may", etc) used in introducing algorithms

\hfill \break

Conformance requirements phrased as algorithms or specific steps that can be implemented in any manner, so long as the end result are equivalent. In particular, the algorithms defined in this specification are intended to be easy to understand and are not necessarily intended to be performant. Implementers are encouraged to either: switch to an L2, optimize, or use Vyper\footnote{Vyperlang: https://vyper.readthedocs.io/en/stable/, Cooper Charles}.

\newpage
\section{Swap Execution}

Presented herein, a derivation of optimal arbitrage between 2 Constant Product Automated Market Maker (CPAAM), Decentralized Exchanges (DEXs) for usage in procedural processes that enable value extraction (i.e. MEV).
This math is applied in the new Sushiswap router for at the source of  Miner Extractable Value (MEV). These trades post user swaps atomically.
Profits are distributed to liquidity providers, in turn giving users better rates. Extracting MEV at source protects user trades from front-run attacks inherently and helps prevent fee spikes from attackers.
\newline 

Slippage: The amount of price impact that a liquidator engenders when trying to sell collateral.
Slippage is denoted \text{$\Delta p(q)$} and is formally defined as the difference between the midpoint price at time $t, p_{\text {mid }}(t)$ and the execution price,  \text{$p_{\text {exec }}(q, t)$} for a traded quantity $q$ at time $$t, \Delta p(q, t)=p_{\text {mid }}(t)-p_{\text {exec }}(q, t)$$. This quantity is usually a function of other variables, such as implied and realized volatility.
\footnote{Slippage is also known as market impact within academic literature.}


\newpage

\section{Mathematical Model}

The following sections describe the derivation of the optimal sizes for post user swap arbitrage between UniswapV2 style exchanges.

\footnote{Benchmarking contracts for establishing a baseline can be found here: https://github.com/manifoldfinance/v2-periphery/tree/master/contracts }



%------------------------------------------------

\section{Constant Product Automated Market Maker}
Constant Product Automated Market Makers (CPAMMs) are smart contracts for token liquidity pairs. UniswapV2 and SushiswapV1 are all governed by the constant product formula given in equation \ref{eqn:constProduct}.

\begin{eqnarray}
	k  &=& R_{\alpha}  R_{\beta}  \label{eqn:constProduct}
\end{eqnarray}

Where \(R_{\alpha}\) corresponds to the Reserves of token \(\alpha\), \(R_{\beta}\) to the Reserves of token \(\beta\) within the pair contract and \( k \) the constant invariant.

A swap trading \( \Delta\beta\) tokens for \( \Delta\alpha \) must satisfy equation \ref{eqn:swap}.

\begin{eqnarray}
	k  &=& (R_{\alpha} - \Delta\alpha)  (R_{\beta} + \gamma\Delta\beta ) \label{eqn:swap}\\
	\gamma  &=& 1 - fee \label{eqn:gamma}
\end{eqnarray}

Where the fee on UniswapV02 and SushiswapV01 is 0.3\% and 0.25\% respectively. For big integer math, equation \ref{eqn:gamma} can be written in the form of equation \ref{eqn:gammaBig}.

\begin{eqnarray}
	\gamma  &=& \frac{997}{1000} \label{eqn:gammaBig}
\end{eqnarray}

From equations \ref{eqn:constProduct} and \ref{eqn:swap} we can derive an equations for the expected amounts out and in, given in equations \ref{eqn:amountOut} and \ref{eqn:amountIn}.

\begin{eqnarray}
	amountOut: \Delta\alpha  &=& \frac{997 R_{\alpha} \Delta\beta }{1000 R_{\beta} + 997 \Delta\beta} \label{eqn:amountOut}\\
	amountIn: \Delta\beta  &=& \frac{1000 R_{\beta} \Delta\alpha }{997 (R_{\alpha} - \Delta\alpha)} \label{eqn:amountIn}
\end{eqnarray}

Post swap, the new liquidity reserves are modified as shown in equations \ref{eqn:reserveA} and \ref{eqn:reserveB}.

\begin{eqnarray}
	R_{\alpha}{new}  &=& R_{\alpha}{old} - \Delta\alpha  \label{eqn:reserveA}\\
	R_{\beta}{new}  &=& R_{\beta}{old} + \Delta\beta  \label{eqn:reserveB}
\end{eqnarray}

Therefore sequential swaps can be simulated off-chain in a deterministic way, given the current liquidity state.

\section{Minimal Procedural DEX Arbitrage}
Establishing a minimal swap for DEX arbitrage consists of a single swap on one DEX followed by the reverse swap on another.

Token amount swap path:
\begin{eqnarray}
	DEX0: \: \: \Delta\beta_{0} \Rightarrow \Delta\alpha_{0}\\
	DEX1: \: \: \Delta\alpha_{0} \Rightarrow \Delta\beta_{1}
\end{eqnarray}

\section{Optimal simple DEX arbitrage size}
From equation \ref{eqn:amountOut}, the definition of a simple DEX arbitrage for CPAMMs can be written in the form of equations \ref{eqn:dex1} and \ref{eqn:dex2}.

\begin{eqnarray}
	\Delta\alpha_{0}  &=& \frac{997 R_{\alpha 0} \Delta\beta_{0} }{1000 R_{\beta 0} + 997 \Delta\beta_{0}} \label{eqn:dex1}\\
	\Delta\beta_{1}  &=& \frac{997 R_{\beta 1} \Delta\alpha_{0} }{1000 R_{\alpha 1} + 997 \Delta\alpha_{0}} \label{eqn:dex2}
\end{eqnarray}

Profit of the arbitrage is simply the amount out of the second trade minus the amount in of the first, shown by equation \ref{eqn:profit}.

\begin{eqnarray}
	profit: y  &=& \Delta\beta_{1} - \Delta\beta_{0} \label{eqn:profit}
\end{eqnarray}


Substituting equation \ref{eqn:dex1} into equation \ref{eqn:dex2}, we get equation \ref{eqn:suby}.

\begin{eqnarray}
	\Delta\beta_{1}  &=& \frac{997 R_{\beta 1} \frac{997 R_{\alpha 0} \Delta\beta_{0} }{1000 R_{\beta 0} + 997 \Delta\beta_{0}} }{1000 R_{\alpha 1} + 997 \frac{997 R_{\alpha 0} \Delta\beta_{0} }{1000 R_{\beta 0} + 997 \Delta\beta_{0}}} \label{eqn:suby}\\
	&=& \frac{997^2 R_{\beta 1}  R_{\alpha 0} \Delta\beta_{0} }{(1000 R_{\beta 0} + 997 \Delta\beta_{0}) 1000 R_{\alpha 1} + 997^2 R_{\alpha 0} \Delta\beta_{0} } \label{eqn:subyMore}
\end{eqnarray}

Since we are looking for the optimal amount In ( \(\Delta\beta_{0}\) ), we can make the following simplifications.

\begin{eqnarray}
	let \: x &=& \Delta\beta_{0}\\
	let \: C_{A} &=& 997^2 R_{\beta 1}  R_{\alpha 0}\\
	let \: C_{B} &=& 1000^2 R_{\beta 0} R_{\alpha 1}\\
	let \: C_{C} &=& 997000  R_{\alpha 1}\\
	let \: C_{D} &=& 997^2  R_{\alpha 0}
\end{eqnarray}

Thus equation \ref{eqn:subyMore} can be reduced to equation \ref{eqn:reduceOut}.

\begin{eqnarray}
	\Delta\beta_{1}  &=& \frac{C_{A} x}{C_{B} + x(C_{C} + C_{D})} \label{eqn:reduceOut}
\end{eqnarray}

Therefore the profit (y), from equation \ref{eqn:profit} can be expressed in terms of the amount In (x), shown in equation \ref{eqn:profit2}.

\begin{eqnarray}
	y  &=& \frac{C_{A} x}{C_{B} + x(C_{C} + C_{D})} - x \label{eqn:profit2}\\
	&=& \frac{C_{A} x - x(C_{B} + x(C_{C} + C_{D}))}{C_{B} + x(C_{C} + C_{D})} \label{eqn:profit3}\\
	&=& \frac{x(C_{A} - C_{B}) - x^2(C_{C} + C_{D})}{C_{B} + x(C_{C} + C_{D})} \label{eqn:profit4}\\
	&=& \frac{x C_{F} - x^2 C_{G} }{C_{B} + x C_{G}} \label{eqn:profit5}
\end{eqnarray}

Where:
\begin{eqnarray}
	C_{F}  &=& C_{A} - C_{B}\\
	C_{G}  &=& C_{C} + C_{D}
\end{eqnarray}

Maximum profit occurs at a turning point i.e. where the gradient or differential is zero, shown in equation \ref{eqn:turn}.

\begin{eqnarray}
	\frac{dy}{dx} = 0 \label{eqn:turn}
\end{eqnarray}

Since we have a complex equation for differentiating, we can use the quotient rule from equation \ref{eqn:quotient}. Numerator and denominator differentials are shown in equations \ref{eqn:fdash} and \ref{eqn:gdash}.

\begin{eqnarray}
	\frac{dy}{dx} &=& \frac{d \frac{ f(x)}{g(x)}}{dx} \label{eqn:turn2}\\
	f(x) &=& x C_{F} - x^2 C_{G} \label{eqn:f}\\
	g(x) &=& C_{B} + x C_{G} \label{eqn:g}\\
	\frac{f(x)}{dx} &=& C_{F} - 2 x C_{G} \label{eqn:fdash}\\
	\frac{g(x)}{dx} &=& C_{G} \label{eqn:gdash}
\end{eqnarray}

Combining the quotient rule with equation \ref{eqn:turn}, we get equation \ref{eqn:quoSolDex}, which expands to equation \ref{eqn:quoSol2}.

\begin{eqnarray}
	f'g &=& g'f \label{eqn:quoSolDex}\\
	(C_{F} - 2 x C_{G})(C_{B} + x C_{G}) &=& C_{G} ( x C_{F} - x^2 C_{G}) \label{eqn:quoSol2}
\end{eqnarray}

Equation \ref{eqn:quoSol2} can be re-arranged to form a generic quadratic equation \ref{eqn:quadRefDex} and so the parameters can be defined for the quadratic solution in equation \ref{eqn:sol}.

\begin{eqnarray}
	x^2 C_{G}^2 + x(2 C_{B} C_{G}) - C_{B} C_{F} &=& 0 \label{eqn:quadRefDex}
\end{eqnarray}

Solution to the optimal simple DEX arbitrage size for a given swap is shown in equation \ref{eqn:sol}.

\begin{eqnarray}
	x^* &=& \frac{-(2 C_{B} C_{G}) \pm \sqrt{(2 C_{B} C_{G})^2 - 4(C_{G}^2)(- C_{B} C_{F})}}{2 C_{G}^2} \label{eqn:sol}
\end{eqnarray}

For positive roots only, this can be reduced to:

\begin{eqnarray}
	x^* &=& \frac{- C_{B} + \sqrt{C_{B} ^2 + C_{B} C_{F}}}{C_{G}} \label{eqn:sol2}
\end{eqnarray}


\chapter{Equivalence Checking}

\subsection{Backrun placement}

By definition, backruns must occur after user to user swap. From a design point of view the simplest place to insert the backrun function would be in the internal $_swap$ function which is called by the other swaps. However, some of the swap variants eg $swapTokensForExactETH$ perform user actions after $_swap$ is called. This is not ideal, as we do not want to interfere with the user swap. Moreover, other swap variants such as $swapExactTokensForTokensSupportingFeeOnTransferTokens$ do not use $_swap$. Backrun functions were therefore placed at the end of each external swap variant. E.g.
\begin{figure}
    \centering
    \caption{Backrun Placement}
    \label{fig:Backrun Placement}
\label{Before swapExactTokensforTokens:1}
\begin{minted}{lexer.py:SolidityLexer -x}
    function swapExactTokensForTokens(
       uint amountIn,
       uint amountOutMin,
       address[] calldata path,
       address to,
       uint deadline
    ) external virtual override ensure(deadline) returns 
    (uint[] memory amounts) {
 amounts = UniswapV2Library.getAmountsOut(factory, amountIn, path);
 require(amounts[amounts.length - 1] 
 >= amountOutMin, 'UniswapV2Router: INSUFFICIENT_OUTPUT_AMOUNT');
    TransferHelper.safeTransferFrom(
            path[0], msg.sender, 
            UniswapV2Library.pairFor(factory, path[0], path[1]), amounts[0]
        );
        _swap(amounts, path, to);
    }
\end{minted}
\end{figure}


\begin{figure}
    \centering
    \caption{Backrun Implementation}
    \label{fig:Backrun Implementation}
\label{After swapExactTokensforTokens:2}
\begin{minted}{lexer.py:SolidityLexer -x}
function swapExactTokensForTokens(
    uint amountIn,
    uint amountOutMin,
    address[] calldata path,
    address to,
    uint deadline
) external virtual override ensure(deadline) returns (uint[] memory amounts) {
    amounts = UniswapV2Library.getAmountsOut(factory, amountIn, path);
    require(amounts[amounts.length - 1] >= amountOutMin, 
    'UniswapV2Router: INSUFFICIENT_OUTPUT_AMOUNT');
    TransferHelper.safeTransferFrom(
        path[0],
        msg.sender, 
        UniswapV2Library.pairFor(factory, path[0], path[1]), amounts[0]
    );
    _swap(amounts, path, to);
    _backrunSwaps(path);
}
\end{minted}
\end{figure}

\newpage 

\subsection{Multiple factories}
Multiple factories (at least 2) are required for the backrun arbitrage. The adoption of multiple factories within the router, lead to some internal function changes. In particular $pairFor$.

\label{CREATE2 Factory:3}
\begin{minted}{lexer.py:SolidityLexer -x}
// calculates the CREATE2 address for a pair without making any external calls
function pairFor(
address factory, 
address tokenA, 
address tokenB
) 
internal pure returns (address pair) {
(address token0, address token1) = sortTokens(tokenA, tokenB);
pair = address(uint160(uint(keccak256(abi.encodePacked(
    hex'ff',
    factory,
    keccak256(abi.encodePacked(token0, token1)),
    // hard coded factory init code hash
    hex'96e8ac4277198ff8b6f785478aa9a39f403cb768dd02cbee326c3e7da348845f'
    )))));
}
\end{minted}
\newpage 

\text{Changes to}
\begin{figure}
    \centering
    \caption{New Factories Implementation}
    \label{fig:New Factories}
\begin{minted}{lexer.py:SolidityLexer -x}

function pairFor(address factory, address tokenA, address tokenB) 
 internal view returns (address pair) {
    bytes memory factoryHash = factory
        == SUSHI_FACTORY ? SUSHI_FACTORY_HASH : BACKUP_FACTORY_HASH;

(address token0, address token1) = _sortTokens(tokenA, tokenB);
   pair = address(uint160(uint(keccak256(abi.encodePacked(
     hex'ff',
     factory,
     keccak256(abi.encodePacked(token0, token1)),
     factoryHash // init code hash
    )))));
}
\end{minted}
\end{figure}

\subsection{Fallback factory}
Since the extra factory is required for the arbitrage, we can use it, for the user, to check for an available swap on the alternate factory if it would otherwise fail on the default factory through slippage.

\label{Fallback Factory:4}
\begin{minted}{lexer.py:SolidityLexer -x}
amounts = UniswapV2Library.getAmountsOut(factory, amountIn, path);
require(amounts[amounts.length - 1]
>= amountOutMin, 'UniswapV2Router: INSUFFICIENT_OUTPUT_AMOUNT');
\end{minted}
Changes to
\begin{figure}
    \centering
    \caption{Fallback Factory Implementation}
    \label{fig:Fallback Factory Implementation}
\begin{minted}{lexer.py:SolidityLexer -x}
address factory = SUSHI_FACTORY;
amounts = _getAmountsOut(factory, amountIn, path);
if(amounts[amounts.length - 1] < amountOutMin){
    // Change 1 -> fallback for insufficient output amount, check backup router
    amounts = _getAmountsOut(BACKUP_FACTORY, amountIn, path);
    require(amounts[amounts.length - 1] 
    >= amountOutMin, 'UniswapV2Router: INSUFFICIENT_OUTPUT_AMOUNT');
    factory = BACKUP_FACTORY;
}
\end{minted}
\end{figure}

\chapter{Math Libraries and BigInt support}

\paragraph{These following sections describe testing various math libraries to accommodate the additional calculations required of the router.}

\subsection{Uint256 overflow}
\text{Optimal arbitrage calculations were overflowing uint256. i.e.}
\label{Uint256 overflow:5}
\begin{minted}{lexer.py:SolidityLexer -x}
uint Cd = reserve0Token1.mul(997).mul(997);
uint Cc = reserve1Token1.mul(997000);
uint Cb = reserve1Token1.mul(reserve0Token0).mul(1000).mul(1000);
uint Ca = reserve1Token0.mul(reserve0Token1).mul(997).mul(997);
uint Cf = Ca - Cb;
uint Cg = Cc + Cd;
uint a = Cg * Cg;
uint b = 2 * Cb * Cg;
uint c = Cb * Cf;
uint d = (b*b) + ( 4 * a * c ); 
\end{minted}

would consistently overflow by $uint b$. Found out through individual checks:
\begin{minted}{lexer.py:SolidityLexer -x}
unchecked {
    uint a = Cg * Cg;
    require(a/Cg == Cg,"a overflow");
    uint b = 2 * Cb * Cg;
    require(b/Cb == 2*Cg ,"b overflow");
    uint c = Cb * Cf;
    require(c/Cb == Cf,"c overflow");
    uint d = (b*b) + ( 4 * a * c );
    require(d/(b*b) == 4*a*c,"d overflow");
}
\end{minted}
\newpage

\subsubsection{ABDKMath}
\text{ABDKMath library was used for a time, as it avoided overflow by dropping to floats.}\footnote{$https://github.com/abdk-consulting/abdk-libraries-solidity$} 
\begin{minted}{lexer.py:SolidityLexer -x}
bytes16 _Cg = ABDKMathQuad.fromUInt(Cg);
bytes16 _a = ABDKMathQuad.mul(_Cg, _Cg);
\end{minted}

\text{However we found this lost precision and failed echidna tests.}


\label{Uint256 overflow:5}
\begin{figure}
    \centering
    \caption{Uint256 overflow:5}
    \label{fig:Echidna Uint56 Overflow Tests}
\begin{lstlisting}[style=Bash]
echidna_mulUint:  
failed!
  Call sequence:
    setX1(1106235220955)
    setX(9390953368914254812617)

echidna_Uint_conversion: 
failed!
  Call sequence:
    setX(10518526264810785485368401065708505)

echidna_divUint:  
failed!
  Call sequence:
    setX(10417774989007224423389698535018119)
    setX1(1)
\end{lstlisting}
\end{figure}

\newpage 
\subsubsection{PRBMath}

We also tried PRBMath\footnote{https://github.com/paulrberg/prb-math/} library. These performed better in echidna tests but still suffered overflow issues.

\begin{figure}
    \centering
    \caption{PRBMath}
    \label{fig:Echidna PRBMath Tests}
\begin{lstlisting}[style=Bash]
echidna_mulUint:  
~ failed!
  Call sequence:
    setX1(1106235220955)
    setX(9390953368914254812617)


echidna_Uint_convertion:  
~ failed!
  Call sequence:
    setX(10518526264810785485368401065708505)


echidna_divUint:  
~ failed!
  Call sequence:
    setX(10417774989007224423389698535018119)
    setX1(1)
\end{lstlisting}
\end{figure}

\subsubsection{Uint512}
\text{Ultimately we settled on Uint512  which both passed echidna and overflow issue.}\footnote{see $github.com/SimonSuckut/Solidity_Uint512/blob/main/contracts/Uint512.sol$}


\begin{figure}
    \centering
    \caption{Uint512 }
    \label{fig:Echidna Uint512 Tests}
\begin{lstlisting}
echidna_mulUint: ~ passed! 
echidna_divUint: ~ passed!
\end{lstlisting}
\end{figure}


\section{Conclusions and Future Work}

\newpage
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\chapter{Bibliography}

\begin{thebibliography}{1}
	\bibitem{[2022]Bacha}
	Sam Bacha, Sandy Bradley.
	OpenMEV source code, \url{github.com/manifoldfinance/OpenMevRouter}.
	Last accessed 20 April 2022
	\bibliographystyle{unsrtnat}
	\bibliography{references}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .
	\newline
	\bibitem{[2020]Angeris:2020}
	Guillermo Angeris, Tarun Chitra, Alex Evans, Stephen Boyd
	\newblock Guillermo Angeris et al. Optimal Routing for Constant Function Market Makers.	arXiv:2204.05238
	\newblock In {\em arXiv 1911.03380}, 26 Jul 2021
	Optimization and Control (math.OC); Trading and Market Microstructure (q-fin.TR)

	\hfill \break
	\bibitem{[2019]Angeris:2019}
	Guillermo Angeris et al. An analysis of Uniswap markets. 2019. arXiv: 1911.03380
	\newblock An analysis of Uniswap markets.
	Mathematical Finance (q-fin.MF); Optimization and Control; Trading and Market Microstructure (q-fin.TR)
	\newblock {\em arXiv: 1911.03380},

	\hfill \break
	\bibitem{[2019]Angeris}
	Guillermo Angeris, Alex Evans, Tarun Chitra
	\newblock Replicating Market Makers
	Mathematical Finance (q-fin.MF); Optimization and Control; Trading and Market Microstructure (q-fin.TR)
	\newblock {\em arXiv:2103.14769}, 26 Mar 2021.

	\hfill \break
	\bibitem{[2021]Tarun:2021}
	Guillermo Angeris, Alex Evans, Tarun Chitra
	\newblock Constant Function Market Makers: Multi-Asset Trades via Convex Optimization
	Mathematical Finance (q-fin.MF); Optimization and Control; Trading and Market Microstructure (q-fin.TR)
	\newblock {\em arXiv:2107.12484 }, 26 Jul 2021]
	\url{https://doi.org/10.48550/arXiv.2107.12484}

	\hfill \break
	\bibitem{[2022]Tarun:2022}
	Guillermo Angeris, Tarun Chitra, Alex Evans, Stephen Boyd
	\newblock Optimal Routing for Constant Function Market Makers
	Optimization and Control (math.OC); Trading and Market Microstructure (q-fin.TR)
	\newblock {\em arXiv:2204.05238}, 11 Apr 2022]
	\url{https://arxiv.org/abs/2204.05238v1}

	\hfill \break
	\bibitem{[2022]Suckut}
	Suckut, Simon
	\newblock Uint512 Solidity Library
	\newblock {\em GitHub}, 11 Apr 2022]
	\url{$https://github.com/SimonSuckut/Solidity_Uint512/blob/main/contracts/Uint512.sol$}



\end{thebibliography}
\end{document}
